Group 9 Paper

### 2021-12-16 paper.Rmd
Representatie tree write up

```{r}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train)), importance = TRUE, type= "classification", ntrees=1000)

@@

```{r}
ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy,fill=variables))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())+guides(fill="none")
```

@@

>>>>

```{r,echo=FALSE}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train)), importance = TRUE, type= "classification", ntrees=1000)

@@

```{r,echo=FALSE}
ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy,fill=variables))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())+guides(fill="none")
```

@@

While working on the random forests, I began to  search for a way to visualize at least one of the trees in the ensemble, in order to more visualization and perhaps get a deeper insight into the method. While I found a way to do it in stack overflow, I also found a recommendation of a paper by Banerjee, et al. called "Identifying representative trees from ensembles" (2012), which was published in the journal of statistical medicine. What we found really interesting is that the example application which was very similar to our application as it was classification problem using kidney cancer data, and there they discuss the importance of not losing the ability to do inference while still having high accuracy.

In the paper Banerjee, et al. discuss how to choose the most representative tree in a n esemble.
